---
title: "Descriptive analsis"
author: "Ibeh Amaka"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This is a sales data containing 34867 observations and 16 variables, first let i will lod all the required data set


```{r}
library(readr)
library(tidyverse)
library(janitor)
library(dplyr)
library(ggplot2)
library(data.table)
```
i will load my data and check the structure of our data

```{r}
sales <- read_csv("C:/Users/ibeha/OneDrive/Desktop/MY R DATASET/Online datatset/salesforcourse-4fe2kehu.csv")
names(sales) 
dim(sales)
str(sales)
```
data pre-processing.
```{r}
sales2= sales[-16]
head(sales2)
sales2 = na.omit(sales2)
```
missing data is too much and i noticed a column added has all the missing data, so i deleted it and check again
i notices the last row has the n.a so i removed 
**lets run our descriptive analysis**
```{r}
table(sales2$`Customer Age`)
age_group = sales2$`Customer Age`
# histogram with added parameters
hist(age_group,
     main="visaulized age groups",
     xlab="age distribution",
     col="darkmagenta",
     xlim = c(15,100), 
     #ylim = c(0,20),
     freq=TRUE
)

```
which month has the highest revenue
```{r}
month_sales = sales2 %>%
  group_by(Month) %>%
  summarize(sum_of_sales = sum(Revenue))

month_sales <- month_sales %>% arrange(desc(sum_of_sales))
month_sales
```
which gender bought which category of product
```{r}
gender_cat <- summarise(group_by(sales2, `Customer Gender`, `Product Category`), n = n())
gender_cat 
#####
ggplot(gender_cat,aes(x=`Product Category` ,y=n,fill=as.factor(`Customer Gender`)))+
  geom_bar(stat="identity",position="dodge")+
  scale_fill_discrete(name="Gender",
                      breaks=c("F", "M"),
                      labels=c("Male", "Female"))+
  xlab("product category")+ylab("frequency")
```
The gender that soend the most, i renamed the columns
```{r}
gender_rev <- aggregate(sales2$Revenue, by=list(sales2$`Customer Gender`), FUN=mean)
gender_rev
setnames(setDT(gender_rev, keep.rownames = FALSE), c(1,2),c("Gender","mean.revenue") )
ggplot(gender_rev, aes(x =  Gender , y = mean.revenue, fill = Gender)) +
  geom_col(position = "dodge")
```
the state that spent more based on product category
```{r}
state_rev <- aggregate(sales2$Revenue, by=list(sales2$State), FUN=mean)
setnames(setDT(state_rev, keep.rownames = FALSE), c(1,2),c("State","mean.revenue") )
state_rev  = state_rev %>% arrange(desc(state_rev$mean.revenue))
ggplot(state_rev, aes(x =  State , y = mean.revenue, fill = State)) +
  geom_col(position = "dodge")
```
country that spent the more on product
```{r}
country_rev <- aggregate(sales2$Revenue, by=list(sales2$Country), FUN=mean)
setnames(setDT(country_rev, keep.rownames = FALSE), c(1,2),c("country","mean.revenue") )
ggplot(country_rev, aes(x =  country , y = mean.revenue, fill = country)) +
  geom_col(position = "dodge")
```